---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
```

### Load data
```{r load-data}
load("brfss2013.RData")
```



* * *

## Part 1: Data
Dataset : [Dataset columns and their details](https://d3c33hcgiwev3.cloudfront.net/_e34476fda339107329fc316d1f98e042_brfss_codebook.html?Expires=1541116800&Signature=BD8jCGrLBjkXRiuI08qinyDD3fvQ4L3ItOJYVWTWNxyJUm7jxqwQtXspJYMsECYzqbPp-65T1aBFb5x0s6t-8jXhlL0tIzP1XHTfQOuSxS3APHNueh4lluL6UOeb06B6A3CD6tki3uYgaqwfJ-JT0ElzPhHYvSf2e4iVpVcEkzU_&Key-Pair-Id=APKAJLTNE6QMUY6HBC5A) 
<br>
[Whether a dataset is randomly sampled](https://www.quora.com/How-do-I-know-if-a-sample-from-a-population-is-a-random-sample-without-making-any-assumptions-on-the-distribution-of-the-population)<br>
[solution](https://github.com/bhunkeler/DataScienceCoursera/blob/master/Statistics%20-%20Duke%20University/001_Introduction_to_Probability_and_Data/Week%205/Lab/Project5/intro_data_prob_project.Rmd)
* * *

## Part 2: Research questions

**Research quesion 1:**

**Research quesion 2:**

**Research quesion 3:**


* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

**Research quesion 1:**

```{r}

```



**Research quesion 2:**

```{r}

```



**Research quesion 3:**

```{r}

```

